---
title: "hw01_gapminder"
author: "yanchao"
output: github_document

---
## Load packages"gapminder"
```{r}
library(gapminder)
##First time should install "gapminder" using R code: Install.pakages("gapminder")
```

## Display the structure of "gapminder"
```{r}
str(gapminder)
```

## Print gapminder to screen
```{r}
class(gapminder)
```

## Only see head or tail of the data
```{r}
head(gapminder)
tail(gapminder)
```

## Query basic info on a data frame
```{r}
names(gapminder)
nrow(gapminder)
dim(gapminder)
length(gapminder)
ncol(gapminder)
```

## Statistical overview
```{r}
summary(gapminder)
```

## Plot interested data


```{r}
plot( lifeExp  ~ pop, gapminder)
```

```{r}
plot( lifeExp ~ gdpPercap, gapminder)
```
## Transform variable
```{r}
plot(lifeExp ~ log(gdpPercap), gapminder)
## these two variables seem to be more liear
```

## Look at the variables inside a data frame
```{r}
head(gapminder$pop)
summary(gapminder$pop)
hist(gapminder$pop)
### If the variables are categorical
table(gapminder$continent)
barplot(table(gapminder$continent))
levels(gapminder$continent)
nlevels(gapminder$continent)
```

## ggplot of the data

### Comparison of the relationship between gdp per cap and life expectation
```{r}
library(tidyverse)
p <- ggplot(filter(gapminder, continent != "Oceania"),
            aes(x = gdpPercap, y = lifeExp)) 
p <- p + scale_x_log10() 
p + geom_point() 
p + geom_point(aes(color = continent)) 
p + geom_point(alpha = (1/3), size = 3) + geom_smooth(lwd = 3, se = FALSE)
p + geom_point(alpha = (1/3), size = 3) + facet_wrap(~ continent) +
  geom_smooth(lwd = 1.5, se = FALSE)
```


### Comparison of the relationship between population and life expectation
```{r}
p <- ggplot(filter(gapminder, continent != "Oceania"),
            aes(x = pop, y = lifeExp)) 
p <- p + scale_x_log10() 
p + geom_point() 
p + geom_point(aes(color = continent)) 
p + geom_point(alpha = (1/3), size = 3) + geom_smooth(lwd = 3, se = FALSE)
p + geom_point(alpha = (1/3), size = 3) + facet_wrap(~ continent) +
  geom_smooth(lwd = 1.5, se = FALSE)
```

## Get help about gapminder

```{r}
??gapminder
``` 
According to `??gapminder`, we can find a help pages about gapminder.